# Priors are normal distributions with mean 0 and standard deviation 10

## Bayes Factor with Indicator Variable Selection

```{r, warning=FALSE,message=FALSE}
iotas = list()
iotan = list()

for(i in 1:n_iterations){
  datalist <- list(
    y = Y1[,i],
    X = ifelse(dat$Group=="A",0,1),
    N = n_participants*n_groups
  )
  
  mdl <- R2jags::jags(data=datalist,parameters.to.save = "iota", model.file = "norm010/IVS.jags",
                      n.iter= 11000, n.chains = 2, n.burnin = 1000, jags.seed = i)
  
  iotas[[i]] = mean(mdl$BUGSoutput$sims.matrix[,"iota"])
  write.table(file="norm010/IVS_1.csv",x=data.frame(iotas[[i]], i),append = TRUE,sep=";",col.names = FALSE)
}

for(i in 1:n_iterations){
  datalist <- list(
    y = Y0[,i],
    X = ifelse(dat$Group=="A",0,1),
    N = n_participants*n_groups
  )
  
  mdl <- R2jags::jags(data=datalist,parameters.to.save = "iota", model.file = "norm010/IVS.jags",
                      n.iter= 11000, n.chains = 2, n.burnin = 1000, jags.seed = i)
  
  iotan[[i]] = mean(mdl$BUGSoutput$sims.matrix[,"iota"])
  write.table(file="norm010/IVS_0.csv",x=data.frame(iotan[[i]], i),append = TRUE,sep=";",col.names = FALSE)
}

```

Under the alternative hypothesis, power is `r round(mean(do.call("c",iotas)>=0.75),2)*100`%, and first-type error is `r round(mean(do.call("c",iotas)<=0.25),2)*100`%.


Under the null hypothesis, power is `r round(mean(do.call("c",iotan)>=0.75),2)*100`%, and first-type error is `r round(mean(do.call("c",iotan)<=0.25),2)*100`%.

```{r}
graph1 = read.csv2("norm010/IVS_1.csv",dec=".")
colnames(graph1) = c("X","BF","iteration")
graph1$hypothesis = "alternative"

graph2 = read.csv2("norm010/IVS_0.csv",dec=".")
colnames(graph2) = c("X","BF","iteration")
graph2$hypothesis = "null"

graph= rbind(graph1,graph2)

ggplot(graph,aes(y=BF,x=iteration,colour=hypothesis))+
  geom_path()+geom_point()

```


## Bayes factor by means of bridgesampling

```{r, warning=FALSE,message=FALSE}
log_posterior_H1 <- function(pars, data) {
  alpha      <- pars["alpha"]
  beta       <- pars["beta"]  
  sigma      <- pars["sigma"] 
  
  out <-
    dnorm(alpha, 1, log = TRUE) +           # prior
    dnorm(beta, 1, log = TRUE) +            # prior
    dgamma(sigma, 1, 0.1, log = TRUE) +     # prior
    sum(dnorm(data$y, alpha+beta*data$X, sigma, log = TRUE)) # likelihood
  
  return(out)
}

log_posterior_H0 <- function(pars, data) {
  alpha      <- pars["alpha"]
  sigma      <- pars["sigma"] 
  
  out <-
    dnorm(alpha, 1, log = TRUE) +           # prior
    dgamma(sigma, 1, 0.1, log = TRUE) +     # prior
    sum(dnorm(data$y, alpha, sigma, log = TRUE)) # likelihood
  
  return(out)
}

bfs0 = list()
bfs1 = list()

for(i in 1:n_iterations){
  
  ## ALTERNATIVE HYPOTHESIS
  
  datalist1 <- list(
    y = Y1[,i],
    X = ifelse(dat$Group=="A",0,1),
    N = n_participants*n_groups
  )
  
  datalist2 <- list(
    y = Y1[,i],
    N = n_participants*n_groups
  )
  
  mdlH1 <- R2jags::jags(data=datalist1,parameters.to.save = c("alpha","beta","sigma"), model.file = "norm010/mdl_H1.jags",
                        n.iter= 11000, n.chains = 2, n.burnin = 1000, jags.seed = i)
  
  mdlH0 <- R2jags::jags(data=datalist2,parameters.to.save = c("alpha","sigma"), model.file = "norm010/mdl_H0.jags",
                        n.iter= 11000, n.chains = 2, n.burnin = 1000, jags.seed = i)
  
  lb_H1 <- c(-Inf,-Inf,0)
  ub_H1 <- c(Inf,Inf,Inf)
  names(lb_H1) <- names(ub_H1) <- c("alpha", "beta","sigma")
  
  lb_H0 <- c(-Inf,0)
  ub_H0 <- c(Inf,Inf)
  names(lb_H0) <- names(ub_H0) <- c("alpha", "sigma")
  
  set.seed(i)
  
  bridge_H1a <- bridge_sampler(samples = mdlH1,
                               log_posterior = log_posterior_H1,
                               data = datalist1,
                               lb = lb_H1, ub = ub_H1)
  bridge_H0a <- bridge_sampler(samples = mdlH0,
                               log_posterior = log_posterior_H0,
                               data = datalist2,
                               lb = lb_H0, ub = ub_H0)
  
  bfs1[[i]] <- bf(bridge_H1a, bridge_H0a)$bf
  write.table(file="norm010/BFS_1.csv",x=data.frame(bfs1[[i]], i),append = TRUE,sep=";",col.names = FALSE)
  
  
  ## NULL HYPOTHESIS
  
  datalist3 <- list(
    y = Y0[,i],
    X = ifelse(dat$Group=="A",0,1),
    N = n_participants*n_groups
  )
  
  datalist4 <- list(
    y = Y0[,i],
    N = n_participants*n_groups
  )
  
  mdlH1 <- R2jags::jags(data=datalist3,parameters.to.save = c("alpha","beta","sigma"), model.file = "norm010/mdl_H1.jags",
                        n.iter= 11000, n.chains = 2, n.burnin = 1000, jags.seed = i)
  
  mdlH0 <- R2jags::jags(data=datalist4,parameters.to.save = c("alpha","sigma"), model.file = "norm010/mdl_H0.jags",
                        n.iter= 11000, n.chains = 2, n.burnin = 1000, jags.seed = i)
  
  lb_H1 <- c(-Inf,-Inf,0)
  ub_H1 <- c(Inf,Inf,Inf)
  names(lb_H1) <- names(ub_H1) <- c("alpha", "beta","sigma")
  
  lb_H0 <- c(-Inf,0)
  ub_H0 <- c(Inf,Inf)
  names(lb_H0) <- names(ub_H0) <- c("alpha", "sigma")
  
  set.seed(i)
  
  bridge_H1b <- bridge_sampler(samples = mdlH1,
                               log_posterior = log_posterior_H1,
                               data = datalist3,
                               lb = lb_H1, ub = ub_H1)
  bridge_H0b <- bridge_sampler(samples = mdlH0,
                               log_posterior = log_posterior_H0,
                               data = datalist4,
                               lb = lb_H0, ub = ub_H0)
  
  bfs0[[i]] <- bf(bridge_H1b, bridge_H0b)$bf
  write.table(file="norm010/BFS_0.csv",x=data.frame(bfs0[[i]], i),append = TRUE,sep=";",col.names = FALSE)
}



# mean(do.call("c",iotas)>=0.75)
# mean(do.call("c",iotas)<=0.25)
# 
# mean(do.call("c",iotan)>=0.75)
# mean(do.call("c",iotan)<=0.25)

```

Under the alternative hypothesis, power is `r round(mean(do.call("c",bfs1)>=3),2)*100`%, and first-type error is `r round(mean(do.call("c",bfs1)<=1/3),2)*100`%.


Under the null hypothesis, power is `r round(mean(do.call("c",bfs0)>=3),2)*100`%, and first-type error is `r round(mean(do.call("c",bfs0)<=1/3),2)*100`%.

```{r}
graph1 = read.csv2("norm010/BFS_1.csv",dec=".")
colnames(graph1) = c("X","BF","iteration")
graph1$hypothesis = "alternative"

graph2 = read.csv2("norm010/BFS_0.csv",dec=".")
colnames(graph2) = c("X","BF","iteration")
graph2$hypothesis = "null"

graph= rbind(graph1,graph2)

ggplot(graph,aes(y=BF,x=iteration,colour=hypothesis))+
  geom_path()+geom_point()

```

## Bayes factor by means of Savage-Dickey Density Ratio


```{r, warning=FALSE,message=FALSE}
Savage_Dickey <- function(x){
  d0          <- dnorm(0,0,10)
  
  beta        <- x$BUGSoutput$sims.matrix[,"beta"]
  
  beta_logspl <- logspline(beta)
  
  return(d0/dlogspline(0,beta_logspl))
}

bfs0 = list()
bfs1 = list()

for(i in 1:n_iterations){
  
  ## ALTERNATIVE HYPOTHESIS
  
  datalist1 <- list(
    y = Y1[,i],
    X = ifelse(dat$Group=="A",0,1),
    N = n_participants*n_groups
  )
  
  mdlH1 <- R2jags::jags(data=datalist1,parameters.to.save = "beta", model.file = "norm010/mdl_H1.jags",
                        n.iter= 11000, n.chains = 2, n.burnin = 1000, jags.seed = i)
  
  bfs1[[i]] <- Savage_Dickey(mdlH1)
  write.table(file="norm010/SD_1.csv",x=data.frame(bfs1[[i]], i),append = TRUE,sep=";",col.names = FALSE)
  
  ## NULL HYPOTHESIS
  
  datalist2 <- list(
    y = Y0[,i],
    X = ifelse(dat$Group=="A",0,1),
    N = n_participants*n_groups
  )
  
  mdlH0 <- R2jags::jags(data=datalist2,parameters.to.save = "beta", model.file = "norm010/mdl_H1.jags",
                        n.iter= 11000, n.chains = 2, n.burnin = 1000, jags.seed = i)
  
  bfs0[[i]] <- Savage_Dickey(mdlH0)
  write.table(file="norm010/SD_0.csv",x=data.frame(bfs0[[i]], i),append = TRUE,sep=";",col.names = FALSE)
}



# mean(do.call("c",iotas)>=0.75)
# mean(do.call("c",iotas)<=0.25)
# 
# mean(do.call("c",iotan)>=0.75)
# mean(do.call("c",iotan)<=0.25)

```

Under the alternative hypothesis, power is `r round(mean(do.call("c",bfs1)>=3),2)*100`%, and first-type error is `r round(mean(do.call("c",bfs1)<=1/3),2)*100`%.


Under the null hypothesis, power is `r round(mean(do.call("c",bfs0)>=3),2)*100`%, and first-type error is `r round(mean(do.call("c",bfs0)<=1/3),2)*100`%.

```{r}
graph1 = read.csv2("norm010/SD_1.csv",dec=".")
colnames(graph1) = c("X","BF","iteration")
graph1$hypothesis = "alternative"

graph2 = read.csv2("norm010/SD_0.csv",dec=".")
colnames(graph2) = c("X","BF","iteration")
graph2$hypothesis = "null"

graph= rbind(graph1,graph2)

ggplot(graph,aes(y=BF,x=iteration,colour=hypothesis))+
  geom_path()+geom_point()

```


## Comparisons by means of WAIC

```{r, warning=FALSE,message=FALSE}
waic0 = list()
waic1 = list()

for(i in 1:n_iterations){
  
  ## ALTERNATIVE HYPOTHESIS
  
  datalist1 <- list(
    y = Y1[,i],
    X = ifelse(dat$Group=="A",0,1),
    N = n_participants*n_groups
  )
  
  mdlH1 <- R2jags::jags(data=datalist1,parameters.to.save = "log_like", model.file = "norm010/log_like_H1.jags",
                        n.iter= 11000, n.chains = 2, n.burnin = 1000, jags.seed = i)
  
  wH1   <- waic(mdlH1$BUGSoutput$sims.list$log_like)
  
  datalist2 <- list(
    y = Y1[,i],
    N = n_participants*n_groups
  )
  
  mdlH0 <- R2jags::jags(data=datalist2,parameters.to.save = "log_like", model.file = "norm010/log_like_H0.jags",
                        n.iter= 11000, n.chains = 2, n.burnin = 1000, jags.seed = i)
  
  wH0   <- waic(mdlH0$BUGSoutput$sims.list$log_like)
  
  ww    <- compare(wH1,wH0)
  
  waic1[[i]] <- ww[1]/ww[[2]]
  write.table(file="norm010/WAIC_1.csv",x=data.frame(waic1[[i]],ww[1],ww[2], i),append = TRUE,sep=";",col.names = FALSE)
  
  ## NULL HYPOTHESIS
  
  datalist3 <- list(
    y = Y0[,i],
    X = ifelse(dat$Group=="A",0,1),
    N = n_participants*n_groups
  )
  
  mdlH1 <- R2jags::jags(data=datalist3,parameters.to.save = "log_like", model.file = "norm010/log_like_H1.jags",
                        n.iter= 11000, n.chains = 2, n.burnin = 1000, jags.seed = i)
  
  wH1   <- waic(mdlH1$BUGSoutput$sims.list$log_like)
  
  datalist4 <- list(
    y = Y0[,i],
    N = n_participants*n_groups
  )
  
  mdlH0 <- R2jags::jags(data=datalist4,parameters.to.save = "log_like", model.file = "norm010/log_like_H0.jags",
                        n.iter= 11000, n.chains = 2, n.burnin = 1000, jags.seed = i)
  
  wH0   <- waic(mdlH0$BUGSoutput$sims.list$log_like)
  
  ww    <- compare(wH1,wH0)
  
  waic0[[i]] <- ww[1]/ww[[2]]
  write.table(file="norm010/WAIC_0.csv",x=data.frame(waic0[[i]],ww[1],ww[2], i),append = TRUE,sep=";",col.names = FALSE)
}



# mean(do.call("c",iotas)>=0.75)
# mean(do.call("c",iotas)<=0.25)
# 
# mean(do.call("c",iotan)>=0.75)
# mean(do.call("c",iotan)<=0.25)

```

Under the alternative hypothesis, power is `r round(mean(do.call("c",waic1)<=(-1)),2)*100`%, and first-type error is `r round(mean(do.call("c",waic1)>=(1)),2)*100`%.


Under the null hypothesis, power is `r round(mean(do.call("c",waic0)<=(-1)),2)*100`%, and first-type error is `r round(mean(do.call("c",waic0)>=(1)),2)*100`%.

```{r}
graph1 = read.csv2("norm010/WAIC_1.csv",dec=".")
colnames(graph1) = c("X","compare","Waic","Error","iteration")
graph1$hypothesis = "alternative"

graph2 = read.csv2("norm010/WAIC_0.csv",dec=".")
colnames(graph2) = c("X","compare","Waic","Error","iteration")
graph2$hypothesis = "null"

graph= rbind(graph1,graph2)

ggplot(graph,aes(y=Waic,x=iteration,colour=hypothesis))+
  geom_path()+geom_point()

```