---
title: "Indicator Variable Selection vs. Bayes Factors"
author: "Michele Scandola"
date: "27 dicembre 2019"
output: 
  html_document: 
    number_sections: yes
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(bridgesampling)
library(R2jags)
library(logspline)
library(loo)

options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)

n_iterations   <- 1000
```

I want to test whether Indicator Variable Selction (Lodewicz) is sensible to priors as Bayes Factors.

# Data simulation

First of all, I am going to simulate a data set.

```{r}
n_participants <- 50
n_groups       <- 2
alpha          <- 10
beta           <- 0.3

dat            <- data.frame(
  ID    = factor(1:(n_participants*n_groups)),
  Group = factor(rep(LETTERS[1:n_groups],each=n_participants))
)

set.seed(1)

dat$y          <- alpha + beta * (as.numeric(dat$Group)-1) + rnorm(n_participants*n_groups,sd=1)

dcohen(y~Group,data=dat)

t.test(y~Group,data=dat)

ggplot(dat,aes(y=y,x=Group))+geom_boxplot()
```

Ok, significant difference.

Let's simulate a data set with no differences between the two groups.
```{r}
set.seed(6)
dat$y          <- alpha + 0 * (as.numeric(dat$Group)-1) + rnorm(n_participants*n_groups,sd=1)

dcohen(y~Group,data=dat)

t.test(y~Group,data=dat)

ggplot(dat,aes(y=y,x=Group))+geom_boxplot()
```

Ok, no significant result.

Let's simulate both cases `r n_iterations` times and see what happens.

```{r}
out            <- list()

Y              <- matrix(ncol=n_iterations,nrow=n_participants*n_groups)

set.seed(1)
Y1             <- apply(Y,2,function(x){alpha + beta * (as.numeric(dat$Group)-1) + rnorm(n_participants*n_groups,sd=1/2)})
set.seed(2)
Y0             <- apply(Y,2,function(x){alpha + 0 * (as.numeric(dat$Group)-1) + rnorm(n_participants*n_groups,sd=1/2)})

out1            <- apply(Y1,2,function(x){t.test(x[dat$Group=="A"],x[dat$Group=="B"])$p.value})
out0            <- apply(Y0,2,function(x){t.test(x[dat$Group=="A"],x[dat$Group=="B"])$p.value})

```

The power is `r round(mean(out1<0.05),2)*100`%.

The first-type error is `r round(mean(out0<0.05),2)*100`%.

Perfect!

```{r child = 'norm001.Rmd'}
```

```{r child = 'norm010.Rmd'}
```

```{r child = 'norm100.Rmd'}
```

```{r child = 'cauchy.Rmd'}
```